### 2017-05-04 Paper_v1.tex
May4_2

\begin{figure}[ht]
\centering
\includegraphics[width=0.7\textwidth]{./Figures/GroupKO.pdf}
\caption{Effect of group knockouts on system. A. Log change in CAT productivity when one (diagonal) or two (off-diagonal) reaction groups are turned off. B. Log change in system state (only species for which data exist) when one (diagonal) or two (off-diagonal) reaction groups are turned off. Total-order effect for each group calculated as the sum of first-order effect and all pairwise effects. Larger and darker circles represent greater effects.}
\label{fig:GroupKO}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.7\textwidth]{./Figures/GroupKO.pdf}
\caption{Effect of group knockouts on system. A. Change in CAT productivity when one (diagonal) or two (off-diagonal) reaction groups are turned off. B. Change in system state (only species for which data exist) when one (diagonal) or two (off-diagonal) reaction groups are turned off. Total-order effect for each group calculated as the sum of first-order effect and all pairwise effects. Larger and darker circles represent greater effects.}
\label{fig:GroupKO}
\end{figure}
